CITK - an architecture and examples of CUDA enabled ITK filters

### 2011-05-24 article/Article.tex
minor extras in article - sending to other authors
allowed cuda to be switched off for IJ

\subsection{Build and install modified ITK}
There are many options available when building ITK. This process has
been tested under Linux and there are a number of changes to defaults
required to avoid limitations to the CUDA development tools. 
\begin{itemize}
  \item Specify location of CUDA SDK.
  \item Turn off SSE options for VNL - see advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
\end{itemize}

\subsection{Build examples}
The Examples subdirectory in the citk distribution includes a
CMakeFile for building all examples and running tests. Location of the
patched ITK, nvcc and CUDA SDK must be provided during configuration.

>>>>

\subsection{Build and install modified ITK}
There are many options available when building ITK. This process has
been tested under Linux and there are a number of changes to defaults
required to avoid limitations to the CUDA development tools. 
\begin{itemize}
  \item Specify location of CUDA SDK. Note that if there is trouble locating libcutil.a, it may be set explicitly under advanced options - CUDA\_CUT\_LIBRARY.
  \item Turn off SSE options for VNL - see advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
  \item Enable ITK\_USE\_REVIEW under advanced options, in order to build all of the tests.
\end{itemize}

\subsection{Build examples}
The Examples subdirectory in the citk distribution includes a
CMakeFile for building all examples and running tests. Location of the
patched ITK, nvcc and CUDA SDK must be provided during
configuration. It is also necessary to set CITK\_USE\_CUDA to ON. This
option has been included to allow the Insight Journal to run some
tests without requiring CUDA development tools.
